---
title: "project 2"
author: "Group 11"
number-sections: true
format: 
  html:
    embed-resources: true
    code-tools: true
  pdf: default
header-includes: |
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
editor_options: 
  chunk_output_type: console
execute:
  echo: true
  eval: true
  warning: false
  message: false
editor: 
  markdown: 
    wrap: sentence
---

```{r}
#packages library
#|echo: false
library(tidyverse)
library(moderndive)
library(gapminder)
library(sjPlot)
library(stats)
library(jtools)
```
# Introduction
(include research question)

# Data preparing & Cleaning

```{r}
#data cleaning
data<-read.csv("dataset11.csv")
data<-na.omit(data)
data$Qualityclass_dummy<-ifelse(data$Qualityclass=="Good",1,0) #for "Good"=1 "Poor"=0
data$Qualityclass <- as.factor(data$Qualityclass)
data$harvested <- as.factor(data$harvested)
```
in this dataset aroma,flavor,acidity,category_two_defects and altitude_mean_meters are continuous variables, Qualityclass and harvested are categorical variables.
#Exploratory Data Analysis
# Illuminating visualizations of the data
```{r}
library(tidyr)
#change formula
data_long <- data %>%
  pivot_longer(cols = c(aroma,flavor,acidity,category_two_defects,altitude_mean_meters),
               names_to = "Variable",
               values_to = "Value")
library(ggplot2)
#boxplot
#continuous
ggplot(data = data_long, aes(x = Qualityclass, y = Value, fill = Qualityclass)) +
  geom_boxplot() +
  facet_wrap(~Variable, scales = "free_y") +  
  theme_minimal() +
  labs(title = "Boxplots of 5 variables by quality",
       x = "qualityclass",
       y = "Value") +
  theme(legend.position = "none")
#categorical
#option 1
ggplot(data, aes(x=Qualityclass ,  y = ..prop.., group=harvested, fill=harvested)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion")
#option 2
ggplot(data, aes(x=harvested ,  y = ..prop.., group=Qualityclass, fill=Qualityclass)) + 
    geom_bar(position="dodge", stat="count") +
    labs(y = "Proportion")
```
#Numerical Summaries
```{r}
#summary
summary(data)
#####need to add a table for summary use gt()
```
#Formal Data Analysis
#Model fitted
original model
$$\ln\left(\frac{p}{1-p}\right) = \alpha + \beta_1 \cdot \textrm{aroma} +
    \beta_2 \cdot \textrm{flavor}+
    \beta_3 \cdot \textrm{acidity}+ 
    \beta_4 \cdot \textrm{defects}+
    \beta_5 \cdot \textrm{meters}+
    \beta_6 \cdot \textrm{harvested}$$
(each variable need to be explain)

```{r}
#model fitted for original
model <- glm(Qualityclass_dummy ~ aroma+flavor+acidity+category_two_defects+altitude_mean_meters+harvested, data = data, family = binomial(link = "logit"))
summary(model)
summ(model)
```
find p-value of category_two_defects and altitude_mean_meters and harvested are higher than 0.05
```{r}
#del category_two_defects variale
model_ctd <- glm(Qualityclass_dummy ~ aroma+flavor+acidity+altitude_mean_meters+harvested, data = data, family = binomial(link = "logit"))
summary(model_ctd)
summ(model_ctd)
```
AIC decreased
```{r}
#del altitude_mean_meters variale
model_amm <- glm(Qualityclass_dummy ~ aroma+flavor+acidity+harvested, data = data, family = binomial(link = "logit"))
summary(model_amm)
summ(model_amm)
```
AIC decreased
```{r}
#del harvested variable
model1 <- glm(Qualityclass_dummy ~ aroma+flavor+acidity, data = data, family = binomial(link = "logit"))
summary(model1)
summ(model1)
####### need a table for summ
```
aroma flavor acidity significant this three varibales will be saved and AIC decreased to min.
optimization model
(final model)
$$\ln\left(\frac{p}{1-p}\right) = \alpha + \beta_1 \cdot \textrm{aroma} +
    \beta_2 \cdot \textrm{flavor}+
    \beta_3 \cdot \textrm{acidity}+ 
    \beta_4 \cdot \textrm{harvested}$$

```{r}
levels(data$Qualityclass) #base on "good"
#for original model
mod1coefs <- round(coef(model), 2)
library(knitr)
confint(model) %>%
  kable()
#for optimization model
mod1coefs1 <- round(coef(model1), 2)
library(knitr)
confint(model1) %>%
  kable()
```
log-odds
```{r}
mod.coef.logodds<-model1 %>%
                  summary() %>%
                  coef()
```

```{r}
#| figure: fig1
#| fig-cap: the log-odds of explanatory variables for quality bad
plot_model(model1, show.values = TRUE, transform = NULL,
           title = "Log-Odds (quality-bad)", show.p = FALSE)
```

```{r}
data<- data%>%
      mutate(logodds.bad = predict(model1))
```

odds
```{r}
model1 %>%
 coef() %>%
  exp()
```
```{r}
#check value
exp(coef(model1))
#odd ratrio for quality bad
plot_model(model1, show.values = TRUE, axis.lim = c(10,1000),
           title = "Odds (quality-bad)", show.p = FALSE)
data<- data%>%
      mutate(odds.bad = exp(logodds.bad))
data<- data%>%
      mutate(prob.bad = fitted(model1))
```
probability
continuous
```{r}
#aroma/acidity/flavor prob
library(ggplot2)
library(tidyr)
library(dplyr)
data_long1 <- data %>%
 pivot_longer(cols = c(aroma, flavor,acidity), names_to = "Type", values_to = "Value")
# plot
ggplot(data = data_long1, aes(x =Value, y =prob.bad, color = Type)) +
 geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
 labs(x = "score", y = "Probability of quality being bad", color = "character Type") +
 theme_minimal()
```

```{r}
library(grid)
library(gridExtra)
#plot

plot_model(model1, type = "pred",terms = "aroma" ,title = "Aroma",
            axis.title = c("aroma", "Prob. of quality being bad"))
plot_model(model1, type = "pred", terms="flavor",title = "Flavor",
            axis.title = c("flavor", "Prob. of quality being bad"))
plot_model(model1, type = "pred",terms = "acidity", title = "Acidity",
            axis.title = c("acidity", "Prob. of quality being bad"))
#merge
grid.arrange(p1[[1]],p2[[1]],p3[[1]],nrow=1)

```
